Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip

### 2014-07-12 trunk/PAPER/simulation.tex
Made changes to meet reviewers' comments

In this section we analyze the results in terms of node coverage and
latency with different network sizes, defect rates and bootstrap
injection points. In particular Figure~\ref{fig:results_coverage}
shows node coverage for \disr{} and Reverse Path Forwarding (RPF) tree
based approach respectively. While the first aim of \disr{} is not to
reach the optimal coverage, we still can observe a quite good
performance as compared to the tree based approach. For low defect
rates, i.e. below 10\%, both approaches reach near ideal coverage for
each of the tested network sizes. Higher defect rates seems to show
more variance for \disr{}. For example at the high 20\% rate \disr{}
ranges from 60\% to 75\% while RPF remains stable at 75\%. However we
can consider this coverage sensibility at higher defect rates as still acceptable
for this first, not yet optimized version of the proposed approach.
Note that defect rates beyond 25\% lead to many disconnected
regions of nodes that \disr{} currently cannot handle. This threshold can be
intuitively related to the fact that in the topologies simulated a
node has (on average) a cardinality of 4 connections to other nodes. This means
that with a defect rate bigger than 25\% a node has at least one of its four
paths as not-working, and this applies (on average) for each node,
thus leading to increased probability of consecutive disconnected
nodes, which eventually create disconnected regions. For example Figure~\ref{fig:net} shows a 30x30 network with a 25\%
defect rate in which the bottom-left part cannot be reached due to
disconnected regions. Note that the remaining defective nodes belonging to
connected regions are successfully surrounded by \disr{} coverage; in any
case, these defect levels should be considered as worst case scenarios, so the
achieved coverage of $0.5$ is a satisfying result for this first
version of \disr{}. On the other hand, the network size seems to have a
limited impact when defect rate does not introduce too many disconnected
regions. 
\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.48\textwidth]{pictures/set1.eps} & 
\includegraphics[width=0.48\textwidth]{pictures/coverage.eps} \\
(a) & (b) 
\end{tabular}
\caption{\disr{} (a) and RPF (b) node coverage}
\label{fig:results_coverage}
\end{figure*}

>>>>

In this section we analyze the results in terms of node coverage and
latency with different network sizes, defect rates and bootstrap
injection points. In particular Figure~\ref{fig:results_coverage}
shows node coverage for \disr{} and Reverse Path Forwarding (RPF) tree
based approach (as adapted in \cite{patwardhan_nanoarch06}) respectively. While the first aim of \disr{} is not to
reach the optimal coverage, we still can observe a quite good
performance as compared to the tree based approach. For low defect
rates, i.e. below 10\%, both approaches reach near ideal coverage for
each of the tested network sizes. Higher defect rates seems to show
more variance for \disr{}. For example at the high 20\% rate \disr{}
ranges from 60\% to 75\% while RPF remains stable at 75\%. However we
can consider this coverage sensibility at higher defect rates as still acceptable
for this first, not yet optimized version of the proposed approach.
Note that defect rates beyond 25\% lead to many disconnected
regions of nodes that \disr{} currently cannot handle. This threshold can be
intuitively related to the fact that in the topologies simulated a
node has (on average) a cardinality of 4 connections to other nodes. This means
that with a defect rate bigger than 25\% a node has at least one of its four
paths as not-working, and this applies (on average) for each node,
thus leading to increased probability of consecutive disconnected
nodes, which eventually create disconnected regions. For example Figure~\ref{fig:net} shows a 30x30 network with a 25\%
defect rate in which the bottom-left part cannot be reached due to
disconnected regions. Note that the remaining defective nodes belonging to
connected regions are successfully surrounded by \disr{} coverage; in any
case, these defect levels should be considered as worst case scenarios, so the
achieved coverage of $0.5$ is a satisfying result for this first
version of \disr{}. On the other hand, the network size seems to have a
limited impact when defect rate does not introduce too many disconnected
regions. 
\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.48\textwidth]{pictures/set1.eps} & 
\includegraphics[width=0.48\textwidth]{pictures/coverage.eps} \\
(a) & (b) 
\end{tabular}
\caption{\disr{} (a) and RPF (b) node coverage}
\label{fig:results_coverage}
\end{figure*}
